Wigglyhedra

### 2024-07-14 draft/wigglyhedra.tex
Removed a todo.

\begin{remark}
\label{rem:wigglyComplexAutomorphism}
The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).\asilata{Check, is the horizontal reflection nothing at all? Is it actually an automorphism?}
\end{remark}

>>>>

\begin{remark}
\label{rem:wigglyComplexAutomorphism}
The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
\end{remark}
